Incentivizing Exploration with Unbiased History

### 2018-11-02 model.tex
Defined reward tape in prelims.

>>>>

\asedit{We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities. This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds, respectively. For each arm $a$ and round $t$, the value in cell $(a,t)$ is drawn independently from Bernoulli distribution $\mD_a$. W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.}
